---
title: "case_study"
author: "Ze Li"
date: "2023-10-10"
output: github_document
---

```{r, include = FALSE message = FALSE, warning=FALSE}
library(tidyverse)
library(ggridges)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

```{r}
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |>
  rename(borough = neighbourhood_group) |>
  mutate(stars = review_scores_location / 2)
```

## Brainstorm questions

- Where are AirBNBs expensive?
  - Borough? Neighborhood?
  - Do other factors (room type) affect price? What about rating?
- How long are AirBNBs active?
  - Are AirBNBs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by location?
- How mandy apts are run by one host?
  - Does that affect price?
  - Does that vary by neighborhood?
- Where are AirBNBs?
  - Borough? Neighborhood?
  - Lat and log?

## Attemp solutions

### Where are AirBNBs expensive?

- some EDA

```{r}
nyc_airbnb |> 
  count(borough)
```

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough~room_type)
#Some modification
nyc_airbnb |> 
  filter(price<1000, room_type=="Entire home/apt") |>  
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(.~borough)
```

### Where in manhattan are apt expensive

```{r}
#Where in manhattan are apt expensive
nyc_airbnb |> 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb |> 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()
```

### Make a map

```{r}
nyc_airbnb |> 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

```{r}
library(leaflet)
```

```{r}
nyc_airbnb |> 
  filter(price < 1000,
         room_type == "Entire home/apt",
         borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> #没有地图
  addCircleMarkers(~long, ~lat, radius = 0.2)
```
